---
title: "Williamson Hall Wells"
author: "John McDaris"
date: "5/14/2021"
output: html_document
---

```{r setup, include=FALSE}
require(tidyverse)
require(lubridate)
require(magrittr)
require(TSAUMN)
require(multitaper)
require(dygraphs)
require(ggplot2)
require(ggpubr)
require(lubridate)
require(anytime)
require(imputeTS)
require(zoo)
require(tidyquant)
```

## Data Ingestion
Grabs the current data file from the website and gets it into memory.  Then remove the first 39 rows of data to get to where the QWTA sensor starts getting real data.  Then change the date columns from character strings to dates.  (Note that OPVL sensor goes online 2 rows later.)


```{r}
Williamson_main <- read.csv("https://monitormywatershed.org/api/csv-values/?result_ids=4494,4495,4496,4497,4498,4499,4605,4606,4832", skip = 42, stringsAsFactors=FALSE) # main data file

N <- 39
Williamson_main <- tail(Williamson_main, -N)
dates <- anytime(Williamson_main$DateTime, tz = "America/Chicago")
Williamson_main$DateTime <- dates
Williamson_main$Decagon_CTD.10_Depth.1 <- Williamson_main$Decagon_CTD.10_Depth.1 / 1000 # convert mm depth to m
Williamson_main$Decagon_CTD.10_Depth.2 <- Williamson_main$Decagon_CTD.10_Depth.2 / 1000 # convert mm depth to m

#dates <- anytime(Williamson_main$DateTimeUTC, tz = "America/Chicago")
#Williamson_main$DateTimeUTC <- dates
```


## Fix Missing Data
Generate index column and interpolate missing data values.

```{r}
#index column
t <- Williamson_main$DateTime - Williamson_main$DateTime[1]
t <- as.double(t)
t <- t/300
t <- t+1
Williamson_main$Index <- t

#new data file with NAs for missing data
y <- nrow(Williamson_main)
z <- Williamson_main$Index[y]

t.new <- 1:z # new time variable with no gaps
x.new <- rep( NA, z) #x variable, initially all NAs
ind <- match (t, t.new) #indices of t.new that match values in t
x.new[ind] <- Williamson_main$DateTime
D <- tibble(Index = t.new, DateTime = x.new)
Williamson_new <- D
dates <- anytime(Williamson_new$DateTime, tz = "America/Chicago")
Williamson_new$DateTime <- dates
Williamson_new$QWTA.Cond.Raw[ind] <- Williamson_main$Decagon_CTD.10_Cond.1
Williamson_new$QWTA.Cond.Cal[ind] <- Williamson_main$Decagon_CTD.10_Cond.3
Williamson_new$QWTA.Depth.Raw[ind] <- Williamson_main$Decagon_CTD.10_Depth.1
Williamson_new$QWTA.Temp[ind] <- Williamson_main$Decagon_CTD.10_Temp.1
Williamson_new$OPVL.Cond.Raw[ind] <- Williamson_main$Decagon_CTD.10_Cond.2
Williamson_new$OPVL.Cond.Cal[ind] <- Williamson_main$Decagon_CTD.10_Cond.4
Williamson_new$OPVL.Depth.Raw[ind] <- Williamson_main$Decagon_CTD.10_Depth.2
Williamson_new$OPVL.Temp[ind] <- Williamson_main$Decagon_CTD.10_Temp.2
Williamson_new$Bar.Press[ind] <- Williamson_main$Bosch_BME280_Pressure

#linear interpolation to generate values for missing data
c.miss <- which(is.na(Williamson_new$DateTime))
f <- na_interpolation(Williamson_new$QWTA.Cond.Raw, option = "linear")
Williamson_new$QWTA.Cond.Raw <- f
f <- na_interpolation(Williamson_new$QWTA.Cond.Cal, option = "linear")
Williamson_new$QWTA.Cond.Cal <- f
f <- na_interpolation(Williamson_new$QWTA.Depth.Raw, option = "linear")
Williamson_new$QWTA.Depth.Raw <- f
f <- na_interpolation(Williamson_new$QWTA.Temp, option = "linear")
Williamson_new$QWTA.Temp <- f
f <- na_interpolation(Williamson_new$OPVL.Cond.Raw, option = "linear")
Williamson_new$OPVL.Cond.Raw <- f
f <- na_interpolation(Williamson_new$OPVL.Cond.Cal, option = "linear")
Williamson_new$OPVL.Cond.Cal <- f
f <- na_interpolation(Williamson_new$OPVL.Depth.Raw, option = "linear")
Williamson_new$OPVL.Depth.Raw <- f
f <- na_interpolation(Williamson_new$OPVL.Temp, option = "linear")
Williamson_new$OPVL.Temp <- f

baro_na <- 1:8007
Williamson_new$Bar.Press[baro_na] <- 0

f <- na_interpolation(Williamson_new$Bar.Press, option = "linear")
Williamson_new$Bar.Press <- f

```
## Unit Conversions 
```{r}
Williamson_new$QWTA.MASL <- 257 - 13.106 + Williamson_new$QWTA.Depth.Raw #depth to MASL - 257masl at wellhead, sensor at 13.106 m depth
Williamson_new$OPVL.MASL <- 257 - 17.983 + Williamson_new$OPVL.Depth.Raw #depth to MASL - 257masl at wellhead, sensor at 17.983 m depth
Williamson_new$Bar.Press <- Williamson_new$Bar.Press * 0.000102 #pascals to m H2O
```



## Well-head Barametric Pressure
```{r}
Williamson_baro <- tail(Williamson_new, -8007)
ggplot(Williamson_baro, aes(x = DateTime, y = Bar.Press)) + geom_point() + geom_smooth(method = "loess", span = 0.05, method.args = list(degree=2), colour = "red") +xlab("Date")+ylab("Barometric Pressure - MASL")
```
```{r}
ggplot(Williamson_baro, aes(x = Bar.Press, y = QWTA.MASL)) + geom_point() + 
  geom_smooth(method='lm', formula= y~x, se = FALSE) + stat_regline_equation(label.y = 245.859, aes(label = ..eq.label..)) + stat_regline_equation(label.y = 245.858, aes(label = ..rr.label..)) + xlab("Barometric Pressure (m H2O)") + ylab("QWTA Water Level (MASL)")
ggplot(Williamson_baro, aes(x = Bar.Press, y = OPVL.MASL)) + geom_point() + geom_smooth(method = 'lm', formula = y~x, se = FALSE) + stat_regline_equation(label.y = 241.335, aes(label = ..eq.label..)) + stat_regline_equation(label.y = 241.33, aes(label = ..rr.label..)) + xlab("Barometric Pressure (m H2O)") + ylab("OPVL Water Level (MASL)")
```




## QWTA Well Visualizations

```{r}
Williamson_QWTA <- Williamson_new[,c(1,2,3,4,5,6,11,12)] #select columns for QWTA well 668848

ggplot(Williamson_QWTA, aes(x = DateTime, y = QWTA.Depth.Raw)) + geom_point() + geom_smooth(method = "loess", span = 0.05, method.args = list(degree=2), colour = "red")

ggplot(Williamson_QWTA, aes(x = DateTime, y = QWTA.MASL)) + geom_point() + geom_smooth(method = "loess", span = 0.05, method.args = list(degree=2), colour = "red")

QWTA_depth.mtm <- spec.mtm(Williamson_QWTA$QWTA.Depth.Raw, deltat = 1/288, dtUnits = "day", nw = 4, k = 8, plot = FALSE, Ftest = TRUE)
gplot.mtm(QWTA_depth.mtm, period = TRUE, trans = "log10")
gplot.mtm.ftest(QWTA_depth.mtm, uci = 0.99, period = TRUE)

ggplot(Williamson_QWTA, aes(x = DateTime, y = QWTA.Cond.Cal)) + geom_point() + geom_smooth(method = "loess", span = 0.05, method.args = list(degree=2), colour = "red")

QWTA_cond.mtm <- spec.mtm(Williamson_QWTA$QWTA.Cond.Cal, deltat = 1/288, dtUnits = "day", nw = 4, k = 8, plot = FALSE, Ftest = TRUE)
gplot.mtm(QWTA_cond.mtm, period = TRUE, trans = "log10")
gplot.mtm.ftest(QWTA_cond.mtm, uci = 0.99, period = TRUE)

ggplot(Williamson_QWTA, aes(x = DateTime, y = QWTA.Temp)) + geom_point() + geom_smooth(method = "loess", span = 0.05, method.args = list(degree=2), colour = "red") + ylim(15, 16)
```

## OPVL Well Visualizations

```{r}
Williamson_OPVL <- Williamson_new[,c(1,2,7,8,9,10,11,13)] #select columns for OPVL well 668849
Williamson_OPVL <- tail(Williamson_OPVL, -2) #remove the two extra rows of non-data for OPVL well

ggplot(Williamson_OPVL, aes(x = DateTime, y = OPVL.Depth.Raw)) + geom_point() + geom_smooth(method = "loess", span = 0.01, method.args = list(degree=2), colour = "red") # water depth measurement

ggplot(Williamson_OPVL, aes(x = DateTime, y = OPVL.Depth.Raw)) + geom_point() + geom_ma(ma_fun = SMA, n=50, linetype = 1, size = 1, color = "red") # water depth measurement

OPVL_depth.mtm <- spec.mtm(Williamson_OPVL$OPVL.Depth.Raw, deltat = 1/288, dtUnits = "day", nw = 4, k = 8, plot = FALSE, Ftest = TRUE)
gplot.mtm(OPVL_depth.mtm, period = TRUE, trans = "log10")
gplot.mtm.ftest(OPVL_depth.mtm, uci = 0.99, period = TRUE)

ggplot(Williamson_OPVL, aes(x = DateTime, y = OPVL.Cond.Cal)) + geom_point() + geom_smooth(method = "loess", span = 0.01, method.args = list(degree=2), colour = "red") # Calibrated Specific conductance measurement

OPVL_cond.mtm <- spec.mtm(Williamson_OPVL$OPVL.Cond.Cal, deltat = 1/288, dtUnits = "day", nw = 4, k = 8, plot = FALSE, Ftest = TRUE)
gplot.mtm(OPVL_cond.mtm, period = TRUE, trans = "log10")
gplot.mtm.ftest(OPVL_cond.mtm, uci = 0.99, period = TRUE)

ggplot(Williamson_OPVL, aes(x = DateTime, y = OPVL.Temp)) + geom_point() + geom_smooth(method = "loess", span = 0.05, method.args = list(degree=2), colour = "red") + ylim(13.5, 14.5)

```

